Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex
More text

\subsection{Experimental Setup}

@@

\subsection{Induced}

What proportion of instances are actually satisfiable as $k$ increases?

@@

\subsection{Non-Induced}

What proportion of instances are actually satisfiable as $k$ increases?

\subsection{Solving from the Top Down}
\section{Conclusion}

>>>>

\subsection{Experimental Setup} \label{section:setup}

@@

@@

We now evaluate our algorithm and show that it is effective in practice, even on the larger subgraph
isomorphism instances. In \cref{figure:runtimes} we give cumulative distribution plots for the
induced and non-induced problems, with $k$ ranging from $0$ to $5$ (we discuss the dotted lines in
this plot below). The results are strong: with $k = 0$ we may solve nearly every instance, whilst
even at $k = 5$ we can solve over $4,000$ instances in both variants.

But are we learning anything about the results---that is, are there instances for which $k = 0$ is
unsatisfiable, but that are satisfiable for small $k$? For the problem families which do not consist
entirely of satisfiable instances, we plot this in \cref{figure:which-k}. In the ``phase'' family,
which consists of instances crafted to be extremely difficult to solve, we are not able to answer
this question, and in the ``scalefree'' family we see no satisfiable instances with low but not zero
$k$ (this is simply due to there being many vertices with loops in some pattern graphs, but no loops
at all in the targets). However, in several of the remaining families we can over double the number
of instances for which exact solutions are known, and gain upper bounds on many more. This is
particularly interesting for the ``images-CVIU11'' family, where the size of the solution has a
direct real-world interpretation in terms of closeness of image matching.

\subsection{Solving from the Top Down}

What would happen if we used our approach to solve the maximum common induced problem? We could
simply start at $k = 0$, and increase $k$ until a solution is found. This would be tackling the
problem in the opposite direction from existing approaches, which work by attempting to construct
larger and larger solutions. The dotted lines in \cref{figure:runtimes} show this approach: the $k
\downarrrow$ is our algorithm, whilst ``MCS'' and ``clique'' are the two algorithms discussed in ??.
Bearing in mind the disclaimer in \cref{section:setup} regarding instances not fitting in RAM, we
see that our approach is able to close over twice as many of these instances as the previous state
of the art. (The same conclusion holds even if every instance which is satisfiable with $k = 0$ is
removed from the dataset.)

\section{Conclusion}
